# Technical Preparation
## Libraries set-up
```{r}
library(dplyr)
library(tm)
library(stm)
library(ggplot2)
library(tidyr)
library(purrr)
#library(ggpubr)
library(ggrepel)
library(tidytext)
library(tidyverse)
library(ggcorrplot)
```

# Versions 
```{r}
sessionInfo()
```
# Data Download & Preparation for STM
```{r}
data <- read_csv("C:/Users/user/Downloads/full_data_cleaned (1).csv")
data <- select(data, -1)
data$room_type <- as.factor(data$room_type)
data$year <- as.factor(data$year)
data$date<-  as.Date(data$date, format ="%Y-%m-%d")
dates_sorted <- data[order(data$date),] %>% select("date")
dates_sorted_uniques<- dates_sorted %>% unique
dates_integer <- seq(1, dim(dates_sorted_uniques)[1], by=1)
dates_df<- data.frame(dates_sorted_uniques, dates_integer)
data<- left_join(data, dates_df, by='date')
data<- data[order(data$date),]
data <- select(data, c("comments", "room_type", "dates_integer"))
```

```{r}
processed <- textProcessor(data$comments, metadata = data, ucp = FALSE,
  stem = FALSE, removestopwords = FALSE, wordLengths = c(2, Inf), verbose=TRUE)
```

# Fig.2 - Possible results of using different thresholds for the elimination of infrequent words
```{r}
plotRemoved(processed$documents, lower.thresh = seq(1, 20, by = 1))
```

```{r}
out <- prepDocuments(processed$documents, processed$vocab, processed$meta, lower.thresh = 20)
docs <- out$documents
vocab <- out$vocab
meta <-out$meta
```


# Number of Topics Optimization
```{r}
system.time({
storage <- searchK(out$documents, out$vocab, K = c(5,10,15,20,25,30), N= 73000,
prevalence =~ room_type + s(dates_integer) + s(dates_integer)*room_type, data = meta, verbose=FALSE, heldout.seed = 17,
init.type= "Spectral",  max.em.its = 75
)})
```

```{r}
system.time({
storage2 <- searchK(out$documents, out$vocab, K = c(35,40), N= 73000,
prevalence =~ room_type + s(dates_integer) + s(dates_integer)*room_type, data = meta, verbose=FALSE, heldout.seed = 17,
init.type= "Spectral",  max.em.its = 75
)})
```

```{r}
storage_30<- storage$results
storage_40<- storage2$results
storage_40<- rbind(storage_30,storage_40) %>% as.data.frame()

```

# Fig.4 Estimation of Residuals, Semantic Coherence, Exclusivity, and Variational lower bound for different numbers of topics
```{r}
library(palmerpenguins)
  
# combined plot with 2 rows and 1 column
par(mfcol = c(2,2))
  
# first single plot
plot(storage_40$K,
     storage_40$residual,
     main = "Residuals",
     type = "b",
     xlab = "Number of Topics (K)",
     ylab = "Residuals",
      col = "#0000AF")
  
# second single plot
plot(storage_40$K,
     storage_40$semcoh,
     main = "Semantic Coherence",
     type = "b",
     col = "#0000AF",
     xlab = "Number of Topics (K)",
     ylab = "Semantic Coherence")

plot(storage_40$K,
     storage_40$exclus,
     main = "Exclusivity",
     type = "b",
     col = "#0000AF",
     xlab = "Number of Topics (K)",
     ylab = "Exclusivity")

plot(storage_40$K,
     storage_40$lbound,
     main = "Lower Bound",
     type = "b",
     col = "#0000AF",
     xlab = "Number of Topics (K)",
     ylab = "Lower Bound")
```

# STM and Topic Proportions
```{r}
STM_35 <- stm(docs, vocab, 35, 
                 prevalence =~ room_type + s(dates_integer) + s(dates_integer)*room_type,
                 data = meta,
                 seed = 17, max.em.its = 75, init.type="Spectral", verbose=FALSE
)
```

```{r}
proportions_table <- make.dt(STM_35)  
top_prop<- summarize_all(proportions_table, mean) %>%  t()
```

# Topic Labelling 
```{r}
labelTopics(STM_35, c(1:35)) 
```

# Mining Thoughts for Unlabelled Topics
 2, 5, 6, 9, 20, 24, 27, 29, 30, 33
```{r}
thoughts2 <- findThoughts(STM_35, texts = meta$comments,
n = 3, topics = 2)$docs[[1]]
thoughts5 <- findThoughts(STM_35, texts = meta$comments,
n = 3, topics = 5)$docs[[1]]
thoughts6 <- findThoughts(STM_35, texts = meta$comments,
n = 3, topics = 6)$docs[[1]]
thoughts9 <- findThoughts(STM_35, texts = meta$comments,
n = 3, topics = 9)$docs[[1]]
thoughts20 <- findThoughts(STM_35, texts = meta$comments,
n = 2, topics = 20)$docs[[1]]
thoughts24 <- findThoughts(STM_35, texts = meta$comments,
n = 3, topics = 24)$docs[[1]]
thoughts27 <- findThoughts(STM_35, texts = meta$comments,
n = 3, topics = 27)$docs[[1]]
thoughts29 <- findThoughts(STM_35, texts = meta$comments,
n = 3, topics = 29)$docs[[1]]
thoughts30 <- findThoughts(STM_35, texts = meta$comments,
n = 3, topics = 30)$docs[[1]]
thoughts33 <- findThoughts(STM_35, texts = meta$comments,
n = 3, topics = 33)$docs[[1]]


par(mfrow = c(1,2))
plotQuote(thoughts2, width = 30,  main = "Topic 2")
plotQuote(thoughts5, width = 30,  main = "Topic 5")

par(mfrow = c(1,2))
plotQuote(thoughts6, width = 30,  main = "Topic 6")
plotQuote(thoughts9, width = 30,  main = "Topic 9")

par(mfrow = c(1,2))
plotQuote(thoughts20, width = 30,  main = "Topic 20")
plotQuote(thoughts24, width = 30,  main = "Topic 24")

par(mfrow = c(1,2))
plotQuote(thoughts27, width = 30,  main = "Topic 27")
plotQuote(thoughts29, width = 30,  main = "Topic 29")

par(mfrow = c(1,2))
plotQuote(thoughts30, width = 30,  main = "Topic 30")
plotQuote(thoughts33, width = 30,  main = "Topic 33")
```


# Mining Thoughts and Key Phrases for each topic for deeper understanding
```{r include=FALSE}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 2)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 6)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 10)$docs[[1]]

```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 11)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 14)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 16)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 22)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 25)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 28)$docs[[1]]
```

```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 12)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 21)$docs[[1]]
```

```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 23)$docs[[1]]
```

```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 34)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 27)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 10, topics = 8)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 24)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 35)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 17)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 7)$docs[[1]]
```

```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics = 30)$docs[[1]]
```

```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =33)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =13)$docs[[1]]
```

```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =19)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =31)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =29)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =4)$docs[[1]]
```

```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =3)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =20)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =26)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =15)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 15, topics =32)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =18)$docs[[1]]
```
```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =1)$docs[[1]]
```

```{r}
findThoughts(STM_35, texts = meta$comments,
n = 5, topics =5)$docs[[1]]
```

# Topic Correlation Analysis
```{r}
corr_35 <- topicCorr(STM_35, verbose = FALSE)
topic_correlation_matrix<- corr_35$cor
dev.new(width=20, height=20, unit="in")
plot(topicCorr(STM_35, cutoff = 0.2))
#qgraph(corr_35$cor, graph = "cor", layout = "spring", minimum = 0.6)
```
```{r}

```

# Covariates Effect Estimation

```{r}
prep <- estimateEffect(1:35 ~ room_type + s(dates_integer) + s(dates_integer)*room_type, STM_35,
meta = out$meta, uncertainty = "Global" )
```

# Year Effects for top 16 topics
```{r}
library(stminsights)
effects <- get_effects(estimates = prep,
                      variable = 'dates_integer',
                      type = 'continuous')
effects$value<- round(effects$value, 0)
effects <- left_join(effects, dates_df, join_by(value == dates_integer))
```


# Accommodation Features

Patio and Garden	-	Topic 12
Noise	-	Topic 21
View from Unit -Topic 23
Accommodation Description - Topic 34
`

```{r}
effects  %>%   filter(topic == c(12,21,23,34))  %>% 
 mutate(topic = as.factor(topic)) %>% 
 ggplot(aes(x = date, y = proportion, color = topic, group = topic, fill = topic)) + 
  geom_line() + 
  #scale_fill_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  #scale_color_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  geom_ribbon(aes(y =proportion , ymin = lower, ymax = upper), alpha = 0.4) +
  #scale_fill_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  #scale_color_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) + 
theme(axis.text.x = element_text(angle = 90,size = 16),axis.text.y = element_text(size = 16), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.grid.major = element_line(size = 0.25, linetype = 'dashed', colour = "grey"), axis.title = element_text(size = 24),legend.text = element_text(size = 16),legend.title = element_text(size = 20))+
 scale_x_date(date_breaks = "3 months")+ 
labs(x = 'Date', y = 'Estimated Topic Proportion', color = 'Airbnb Features', group = 'Airbnb Features', fill = 'Airbnb Features') + scale_fill_discrete(labels=c('Patio and Garden', 'Noise', "View from Unit", "Accommodation Description"))

ggsave("C:/Users/user/Documents/UOM/Dissertation/Coding/Saved_graphs/AIRBNB_Feature_new.png",
  width = 40,
  height = 20,
  units =  "cm",
  dpi = 320)
```

# Experience Features
General experience	Experience description	Topic 22
Overall word of mouth	Experience description	Topic 25
General recommendation	Experience description	Topic 14
Home Away from Home	Experience description	Topic 11


```{r}
effects  %>%   filter(topic == c(22,25,14,11))  %>% 
 mutate(topic = as.factor(topic)) %>% 
 ggplot(aes(x = date, y = proportion, color = topic, group = topic, fill = topic)) + 
  geom_line() + 
  #scale_fill_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  #scale_color_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  geom_ribbon(aes(y =proportion , ymin = lower, ymax = upper), alpha = 0.4) +
  #scale_fill_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  #scale_color_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) + 
theme(axis.text.x = element_text(angle = 90,size = 16),axis.text.y = element_text(size = 16), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.grid.major = element_line(size = 0.25, linetype = 'dashed', colour = "grey"), axis.title = element_text(size = 24),legend.text = element_text(size = 16),legend.title = element_text(size = 20))+
 scale_x_date(date_breaks = "3 months")+ 
labs(x = 'Date', y = 'Estimated Topic Proportion', color = 'Experience description', group = 'Experience description', fill = 'Experience description') + scale_fill_discrete(labels=c('Home Away from Home', 'General recommendation', "General experience", "Overall word of mouth"))

ggsave("C:/Users/user/Documents/UOM/Dissertation/Coding/Saved_graphs/Experience description_final.png",
  width = 40,
  height = 20,
  units =  "cm",
  dpi = 320)
```

## Host - Guest relationship Features
Hosts' response	Host	Topic 3
Host advice?	Host	Topic 20
Check-in 	Host	Topic 26
Complimentary things	Host	Topic 15

```{r}
effects  %>%   filter(topic == c(3,20,26,15))  %>% 
 mutate(topic = as.factor(topic)) %>% 
 ggplot(aes(x = date, y = proportion, color = topic, group = topic, fill = topic)) + 
  geom_line() + 
  #scale_fill_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  #scale_color_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  geom_ribbon(aes(y =proportion , ymin = lower, ymax = upper), alpha = 0.4) +
  #scale_fill_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  #scale_color_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) + 
theme(axis.text.x = element_text(angle = 90,size = 16),axis.text.y = element_text(size = 16), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.grid.major = element_line(size = 0.25, linetype = 'dashed', colour = "grey"), axis.title = element_text(size = 24),legend.text = element_text(size = 16),legend.title = element_text(size = 20))+
 scale_x_date(date_breaks = "3 months")+ 
labs(x = 'Date', y = 'Estimated Topic Proportion', color = 'Host-Guest Relationship', group = 'Host-Guest Relationship', fill = 'Host-Guest Relationship') + scale_fill_discrete(labels=c('Complimentary things', 'Host advice', "Check-in", "Hosts' response"))

ggsave("C:/Users/user/Documents/UOM/Dissertation/Coding/Saved_graphs/host_guest.png",
  width = 40,
  height = 20,
  units =  "cm",
  dpi = 320)
```


# Location Features
Neighbourhood attractiveness	Location	Topic 30
Tourist attractions and car parking	Location	Topic 33
Shopping	Location	Topic 13
Accessible Location	Location	Topic 19

```{r}
effects  %>%   filter(topic == c(30,33,13,19))  %>% 
 mutate(topic = as.factor(topic)) %>% 
 ggplot(aes(x = date, y = proportion, color = topic, group = topic, fill = topic)) + 
  geom_line() + 
  #scale_fill_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  #scale_color_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  geom_ribbon(aes(y =proportion , ymin = lower, ymax = upper), alpha = 0.4) +
  #scale_fill_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) +
  #scale_color_manual(values=c("#7F58AF", "#64C5EB", "#E84D8A", "#FEB326")) + 
theme(axis.text.x = element_text(angle = 90,size = 16),axis.text.y = element_text(size = 16), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.grid.major = element_line(size = 0.25, linetype = 'dashed', colour = "grey"), axis.title = element_text(size = 24),legend.text = element_text(size = 16),legend.title = element_text(size = 20))+
 scale_x_date(date_breaks = "3 months")+ 
labs(x = 'Date', y = 'Estimated Topic Proportion', color = 'Location', group = 'Location', fill = 'Location') + scale_fill_discrete(labels=c('Shopping', 'Accessible Location', "Neighbourhood attractiveness", "Tourist attractions and car parking"))

ggsave("C:/Users/user/Documents/UOM/Dissertation/Coding/Saved_graphs/location.png",
  width = 40,
  height = 20,
  units =  "cm",
  dpi = 320)
```

# Room type differences 
Patio and Garden	-	Topic 12
Noise	-	Topic 21
View from Unit -Topic 23
Accommodation Description - Topic 34

```{r}
png(filename="C:/Users/user/Documents/UOM/Dissertation/Coding/Saved_graphs/Differences.png",
    width=30, height=15, units="cm", res=320)
par(mfcol = c(2,2))

# Accomodation Features
plot(prep, covariate = "room_type", topics = c(12, 21, 23,34),
model = STM_35, method = "difference",
cov.value1 = "Private room", cov.value2 = "Entire home/apt",
xlab = "More Entire home/apt  ...  More Private room",
main = "Effect of Room Type on Accomodation Features Topics Proportions",
xlim = c(-.02, .02), labeltype = "custom",
custom.labels = c('Patio and Garden', 'Noise','View from Unit', "Accommodation Description"))

# Experience 
plot(prep, covariate = "room_type", topics = c(22, 25, 14, 11),
model = STM_35, method = "difference",
cov.value1 = "Private room", cov.value2 = "Entire home/apt",
xlab = "More Entire home/apt  ...  More Private room",
main = "Effect of Room Type on Experience Description Topics Proportions",
xlim = c(-.02, .02), labeltype = "custom",
custom.labels = c('General experience', 'Overall word of mouth','General recommendation', "Home Away from Home"))

plot(prep, covariate = "room_type", topics = c(3, 20, 26, 15),
model = STM_35, method = "difference",
cov.value1 = "Private room", cov.value2 = "Entire home/apt",
xlab = "More Entire home/apt  ...  More Private room",
main = "Effect of Room Type on Host-Guest Relationship Topics Proportions",
xlim = c(-.02, .02), labeltype = "custom",
custom.labels = c('Hosts response', 'Host advice','Check-in', "Complimentary things"))

plot(prep, covariate = "room_type", topics = c(30, 33, 13, 19),
model = STM_35, method = "difference",
cov.value1 = "Private room", cov.value2 = "Entire home/apt",
xlab = "More Entire home/apt  ...  More Private room",
main = "Effect of Room Type on Location Topics Proportions",
xlim = c(-.02, .02), labeltype = "custom",
custom.labels = c('Neighbourhood attractiveness', 'Tourist attractions and car parking','Shopping', "Accessible Location"))
dev.off()
```



# Topic Correlation Analysis
```{r}
library(sna)
library(igraph)
library(visNetwork)
tc<- topicCorr(STM_35)
topic_corr_analysis <- topicCorr(STM_35, cutoff=0.05)
topic_corr_analysis <-  topic_corr_analysis$cor
relations <- as.matrix(topic_corr_analysis)

rel_search <- function(x) {ifelse(x>0,x,0)}

res_save<-apply(relations, 2, rel_search) 

#res_save <- relations

nodeInfo <- read.csv("C:/Users/user/Documents/UOM/Dissertation/Coding/Node_description_csv.csv",header=TRUE,stringsAsFactors=FALSE, sep=";")
colnames(nodeInfo) = c("Topic_N" ,"Topic.Name","Class","Proportion" )
nodeInfo <- nodeInfo[order(nodeInfo$Topic_N),]
network <- graph_from_adjacency_matrix(res_save, mode='undirected', diag = FALSE, weighted = TRUE)

w<- E(network)$weight*75
LO =  layout_nicely(network)


png(filename="C:/Users/user/Documents/UOM/Dissertation/Coding/Saved_graphs/corr_plot2.png",
    width=150, height=150, units="cm", res=320)
plot(network, 
     #layout= LO, 
     vertex.label=nodeInfo$Topic.Name ,
      vertex.label.font=2,  
     vertex.label.family="Times",
     vertex.color = as.factor(nodeInfo$Class ),
     vertex.size= nodeInfo$Proportion*350,
     vertex.label.cex=5,
     edge.width=w,
     edge.color="grey"
     )


```

# Word Frequencies for each Topic

```{r}
plot_freq_words = function(beta){
    beta %>% 
    with_groups(Label, top_n, beta, n = 5) %>% 
    filter(beta >= .02) %>% 
    mutate(topic = as.factor(Label)) %>% 
    ggplot(aes(x = reorder(term, beta), y = beta, fill = Label)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(y = "Probability", x = NULL) +
    guides(fill = "none") +
    scale_fill_viridis_d() +
    scale_y_continuous(breaks = seq(0, 1, .1)) +
    facet_wrap(~topic, scales = "free")+
    theme(text=element_text(face="bold", size=20), axis.text.y =element_text(face="bold", size=16) )
}
library(readxl)
topic_names <- read_excel("C:/Users/user/Documents/UOM/Dissertation/Coding/topic_labels.xlsx")
beta_35 <-tidy(STM_35, matrix = "beta")
beta_35 <-left_join(beta_35, topic_names, by='topic')
plot_freq_words(beta_35)

ggsave("C:/Users/user/Documents/UOM/Dissertation/Coding/Saved_graphs/word_frequency.png",
  width = 100,
  height = 100,
  units =  "cm",
  dpi = 320)
```